---
title: "COMPSCIX 415.2 Homework 3"
author: "Jonathan Lee"
date: "2/13/2018"
output: html_notebook
---

```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(nycflights13)
```

###3.8.1
1. This is an example of overplotting. So it under represents how many points are actually at each spot. I would use `geom_jitter` to show a better representation.
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_jitter()
```

2. The paramters of `geom_jitter` that control the amount of jittering are width and height.
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_jitter(width = 9, height = 0)
```

3. `geom_count` gives us different sized points depending on the amount of overlapping points. Both methods are ways to better view overlapping points. `geom_count` might have an area that has a large amount of points that can cover other points though, so it might not always be better to use it.
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_count()
```

4. The default position for geom_boxpot is dodge. As you can see below, the plots look the same with and without ```position = "dodge"```.
```{r}
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = fl, y = cty), position = "dodge")
```
```{r}
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = fl, y = cty))
```

###3.9.1
2. ```labs()``` allows you to modify the title, axis, legend, and plot labels. You can rename them.

4. The plot shows there is positive correlation between a car's city mpg and highway mpg.  
As you can see without the ```coord_fixed()``` the x-axis distances are not the same as y-axis distances, so it can skew how people interpret data. Without ```coord_fixed()``` it looks like the city mpg increases faster than highway mpg.  
```geom_abline``` adds in a line based on the parameters you enter into slope and intercept. As default, it makes the intercept = 0 and slope = 1. You can use it as a reference line when comparing the rest of the plot.


```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() +
  coord_fixed()
```

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() 
```

###4.4
1. The code doesn't work because when you call it again, there is a typo. Instead of an "i", there was a typo and they used "ı" instead.  

2. Fixed Code
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

filter(mpg, cyl == 8)
filter(diamonds, carat > 3)
```

###5.2.4  
1.1
```{r}
filter(flights, arr_delay >= 120)
```
1.2 
```{r}
filter(flights, dest %in% c("IAH","HOU"))
```



