---
title: "COMPSCIX 415.2 Homework 3"
author: "Jonathan Lee"
date: "2/13/2018"
output: html_notebook
---

```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(nycflights13)
```

###3.8.1
1. This is an example of overplotting. So it under represents how many points are actually at each spot. I would use `geom_jitter` to show a better representation.
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_jitter()
```

2. The paramters of `geom_jitter` that control the amount of jittering are width and height.
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_jitter(width = 9, height = 0)
```

3. `geom_count` gives us different sized points depending on the amount of overlapping points. Both methods are ways to better view overlapping points. `geom_count` might have an area that has a large amount of points that can cover other points though, so it might not always be better to use it.
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_count()
```

4. 
```{r}
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = drv, y = hwy), position = "dodge")
```