---
title: "COMPSCIX 415.2 Homework 3"
author: "Jonathan Lee"
date: "2/13/2018"
output:
  html_document:
    df_print: paged
    self_contained: TRUE
---

```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(nycflights13)
```

###3.8.1
* 1. This is an example of overplotting. So it under represents how many points are actually at each spot. I would use `geom_jitter` to show a better representation.
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_jitter()
```

* 2. The paramters of `geom_jitter` that control the amount of jittering are width and height.
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_jitter(width = 9, height = 0)
```

* 3. `geom_count` gives us different sized points depending on the amount of overlapping points. Both methods are ways to better view overlapping points. `geom_count` might have an area that has a large amount of points that can cover other points though, so it might not always be better to use it.
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_count()
```

* 4. The default position for geom_boxpot is dodge. As you can see below, the plots look the same with and without ```position = "dodge"```.
```{r}
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = fl, y = cty), position = "dodge")
```
```{r}
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = fl, y = cty))
```

###3.9.1
* 2. ```labs()``` allows you to modify the title, axis, legend, and plot labels. You can rename them.  

* 4. The plot shows there is positive correlation between a car's city mpg and highway mpg.  
As you can see without the ```coord_fixed()``` the x-axis distances are not the same as y-axis distances, so it can skew how people interpret data. Without ```coord_fixed()``` it looks like the city mpg increases faster than highway mpg.  
```geom_abline``` adds in a line based on the parameters you enter into slope and intercept. As default, it makes the intercept = 0 and slope = 1. You can use it as a reference line when comparing the rest of the plot.


```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() +
  coord_fixed()
```

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() 
```

###4.4
* 1. The code doesn't work because when you call it again, there is a typo. Instead of an "i", there was a typo and they used "ı" instead.  

* 2. Fixed Code
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

filter(mpg, cyl == 8)
filter(diamonds, carat > 3)
```

###5.2.4  
* 1.1
```{r}
filter(flights, arr_delay >= 120)
```
* 1.2 
```{r}
filter(flights, dest %in% c("IAH","HOU"))
```
* 1.3 We'll first use ```airlines``` to get the list of airlines with their respective abbreviations.
```{r}
airlines
filter(flights, carrier %in% c("UA","AA","DL"))
```
* 1.4
```{r}
filter(flights, month %in% c(7,8,9))
```

* 1.5
```{r}
filter(flights, dep_delay <= 0 & arr_delay > 120)
```

* 1.6
```{r}
filter(flights, dep_delay >= 60 & arr_delay < dep_delay - 30)
```

* 1.7
```{r}
filter(flights, between(dep_time, 0, 600))
```

* 2. ```between()``` gives us the values that are between the two arguments. It is inclusive. (I had already used it for 1.7. I guess I was supposed to use ```>= 0 & <= 600```)

* 3. There are 8255 flights that have a missing ```dep_time```. Other variables that are missing are ```dep_delay```, ```arr_time```, ```arr_delay```, ```air_time```, and occasionally ```tailnum```. These might represent canceled flights.
```{r}
filter(flights, is.na(dep_time))
```

* 4. ```NA ^ 0``` is not missing because whenever you put anything to the zero power, it is always equal to 1.
```NA | TRUE``` is not missing either because the OR operator just requires one thing to be TRUE, and in this case, since one of the arguments is TRUE, it is not missing.
```FALSE & NA``` is not missing because for the AND operator, as soon as one argument is FALSE, the entire thing is FALSE.  
Unfortunately I cannot figure out the general rule due to ```NA * 0``` giving us ```NA```. Originally figured it was just if the expression always had the same result regardless of what you replace NA with, it would be fine, but anything multiplied by 0 should be equal to 0.

###5.4.1
* 1. The most straightforward way would be to just list out the columns you want to select.
```{r}
select(flights, dep_time, dep_delay, arr_time, arr_delay)
```
I had considered using ```contains()``` but doing this would end up grabbing ```sched_dep_time``` and/or ```sched_arr_time``` too. This same problem would arise from grabbing all the columns from ```dep_time``` to ```arr_delay```.  

We could also use the column numbers.
```{r}
select(flights, c(4,6,7,9))
```

* 2. It returns the same result as if you only called it once.
```{r}
select(flights, dep_time, dep_delay, dep_time, dep_time)
```

* 3. ```one_of()``` when used in conjunction with select, lets you select all the columns with names in a character vector. So in the example, you won't have to type all the column names again, and you'll get the year, month, day, dep_delay, and arr_delay columns.
```{r}
vars <- c("year", "month", "day", "dep_delay", "arr_delay")
select(flights, one_of(vars))
```

* 4. I expected it not grab any columns due to none of the columns having the word "TIME" in all caps. By default it ignores case. In order to change the default you need to use ```ignore.case = FALSE```
```{r}
select(flights, contains("TIME"))
```

```{r}
select(flights, contains("TIME", ignore.case = FALSE))
```


