---
title: "COMPSCIX 415.2 Homework 7"
author: "Jonathan Lee"
date: "3/19/2018"
output:
  html_document:
    df_print: paged
    self_contained: yes
    toc: yes
  html_notebook:
    toc: yes
---

```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(broom)
```

###Exercise 1
There are 1460 observations and 81 columns
```{r}
train <- read_csv("E:/Chrome Downloads/train.csv")
glimpse(train)
```

###Exercise 2
```{r}
set.seed(29283)
train_set <- train %>% sample_frac(.7)
test_set <- train %>% filter(!(train$Id %in% train_set$Id))
```

###Exercise 3

```{r}
mod_0 <- lm(SalePrice ~ 1, data = train_set)

# Double-check that the average SalePrice is equal to our model's coefficient
mean(train_set$SalePrice)
tidy(mod_0)

# Check the R-squared
glance(mod_0)
```

###Exercise 4

```{r}
mod_all <- lm(SalePrice ~ GrLivArea + OverallQual + Neighborhood, data = train_set)
tidy(mod_all)
glance(mod_all)
```

Questions:  
 * The coefficient for ```GrLivArea``` that I obtained was 62.78, which means that for every 1 increase in above ground living area square feet, the ```SalePrice``` will go up by $62.78. For ```OverallQual```, I obtained 21692.23, which means that for every 1 unit increase of overall material and finish quality, the ```SalePrice``` goes up by $21692.23  
 * The coefficient for ```NeighborhoodBrkSide``` is -14064.37. This means that if the house in the that specific neighborhood, the ```SalePrice``` will drop by $14064.37  
 * The features seem signficiant based on the p-values and R-Squared values  
 * I would say the features are also practically signficant as they do have a big impact on the ```SalePrice```  
 * It appears to be a good fit
 
###Exercise 5
We get an RMSE of 41915.27. We need to take a look at the range of ```SalePrice``` to see if this is considered high or low. As the range is from 34900 - 755000, we can say this is a relatively small RMSE.
```{r}
test_predictions <- predict(mod_all, newdata = test_set)
rmse <- sqrt(mean((test_predictions - test_set$SalePrice)^2))
max(test_set$SalePrice)
min(test_set$SalePrice)
```

###Exercise 7
It seems that the the linear model does an ok job of modeling it, but when there are outlier values, it does cause a slight shift in the outlier direction.
```{r}
sim1a <- tibble(
  x = rep(1:10, each = 3),
  y = x * 1.5 + 6 + rt(length(x), df = 2)
)

firstmodel <- tidy(lm(y ~ x, data = sim1a))

ggplot() +
  geom_point(mapping = aes(x = sim1a$x, y = sim1a$y)) +
  geom_abline(intercept = firstmodel$estimate[1], slope = firstmodel$estimate[2] )
```






