---
title: "COMPSCIX 415.2 Homework 6"
author: "Jonathan Lee"
date: "3/12/2018"
output:
  html_document:
    df_print: paged
    toc: TRUE
    self_contained: TRUE
---


```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(mosaicData)
```

###Exercise 1
```{r}
data(Whickham)
```
1. The 3 variables in this data set are the following
  *  ```outcome``` which indicates the survival status after 20 years
  *  ```smoker``` which indicates whether the person is a smoker
  *  ```age``` which indicates how old the person was at the time of the first survey
2. There are 1314 observations. Each observation is a woman.  
3.rename(Smoker = 'smoker == "Yes"', Alive = 'outcome == "Alive"') %>%
```{r}
Whickham %>%
  count(smoker == "Yes", outcome == "Alive") %>%
  rownames_to_column %>%
  select(rowname, n) %>%
  spread(rowname, n) %>%
  rename("Non-Smoker, Dead" = '1', "Non-Smoker, Alive" = '2', "Smoker, Dead" = '3', "Smoker, Alive" = '4') %>%
  gather() %>%
  ggplot() + 
    geom_bar(mapping = aes(x = key, y = value), stat="identity") +
    xlab("Status") + 
    ylab("Amount")
```

4. I couldn't really figure out how to do this section. This was my attempt.
```{r}
Whickham %>%
  mutate(age_fct = factor(case_when(Whickham$age <= 44 ~ '<=44',
                     Whickham$age > 44 & Whickham$age <= 64 ~ '>44 & <= 64',
                     Whickham$age > 64 ~ '>64'))) %>%
  group_by(age_fct) %>%
  count(smoker == "Yes", outcome == "Alive") %>%
  rownames_to_column %>%
  ggplot() +
  geom_bar(mapping = aes(x = rowname, y = n), stat = "identity") + 
  facet_grid(.~age_fct)
```

###Exercise 2

1. 
```{r}
n <- 10000
gamma_samp <- tibble(x = rgamma(n, shape = 1, scale = 2))
ggplot() +
  geom_histogram(mapping = aes(x = gamma_samp))
```

2. Mean = 2.007, SD = 2.054
```{r}
mean_samp <- gamma_samp %>% .[['x']] %>% mean()
sd_samp <- gamma_samp %>% .[['x']] %>% sd()
```

3. Mean = 2.159, SD = 1.981
```{r}
small_gamma_samp <- tibble(x = rgamma(30, shape = 1, scale = 2))
ggplot() +
  geom_histogram(mapping = aes(x = small_gamma_samp))

mean_small_gamma_samp <- small_gamma_samp %>% .[['x']] %>% mean()
sd_small_gamma_samp <- small_gamma_samp %>% .[['x']] %>% sd()
```

4. 
```{r}
mean_samp <- rep(NA, 10000)

for(i in 1:10000) {
  g_samp <- rgamma(30, shape = 1, scale = 2)
  mean_samp[i] <- mean(g_samp)
}

mean_samp <- tibble(mean_samp)
```

5. 
```{r}
ggplot() + 
  geom_histogram(mapping = aes(x = mean_samp))
```

6. Mean = 2.004, SD = 0.369
```{r}
mean_mean_samp <- mean(mean_samp$mean_samp)
sd_mean_samp <- sd(mean_samp$mean_samp)
```

7. At first I was slightly surprised by the Standard Deviation not being close to 2, but then I thought about it a bit more and remembered that this isn't taking the SD of the gamma distribution, but of the means of the various gamma distributions we created. This made more sense as the means shouldn't differ that much.

8. Mean = 2.001, SD = .114
This lines up as ```2/sqrt(300)``` is 0.115
```{r}
mean_samp_300 <- rep(NA, 10000)

for(i in 1:10000) {
  g_samp <- rgamma(300, shape = 1, scale = 2)
  mean_samp_300[i] <- mean(g_samp)
}

mean_samp_300 <- tibble(mean_samp_300)

ggplot() + 
  geom_histogram(mapping = aes(x = mean_samp_300))

mean_mean_samp_300 <- mean(mean_samp_300$mean_samp_300)
sd_mean_samp_300 <- sd(mean_samp_300$mean_samp_300)
```


