---
title: "Homework 2"
output:
  html_document:
    self_contained: true
---

```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
```

3.2.4  

1. The code shows us a blank canvas.
```{r} 
ggplot(data = mpg)
```

2. There are 234 rows and 11 columns
```{r}
glimpse(mpg)
```

3. The drv variable categorizes the cars into "f" for front-wheel drive, "r" for rear-wheel drive, and "4" for 4-wheel drive.  


4.
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = hwy, y = cyl))
```

5. Plotting this would be not useful as this data would be better arranged in a table. The plot shows points at each type of drive for each class of car. A table can accomplish this task better.
```{r}
ggplot(data=mpg) +
  geom_point(mapping = aes(x = class, y = drv))
```

3.3.1  
1. The reason the points are not blue is because the 'color = "blue"' section was included in the mapping section of the code. In order to turn the points blue, you need to separate it out like below.
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```

2. Categorical Variables: manufacturer, model, trans, drv, fl, class  
Continuous Variables: displ, year, cyl, cty, hwy  
(I can see arguments for displ, year, and cyl to be Categorical too)  
You can use either the following code to get an idea of what the dataset looks like or use View(mpg). When I tried to include View(mpg) as a code chunk the file would give an error while trying to Knit.
```{r}
glimpse(mpg)
```

3. For color and size, the variable can fall in between values displayed by the legend. It all scales depending on what the value is. For shape, you cannot map a continuous variable to a shape. It will give you an error.  
A categorical variable will have a specific color, size, and shape for each unique variable.
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = cty))
```
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, size = cty))
```
```{r eval = FALSE}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, shape = cty))
```

4. If you map the same variable to multiple aesthetics, it will just apply them all to the variable. It will apply the same aesthetics as if only one was assigned. For example, it will give it the same shade of blue as it was given when you only map color, and it will give it the same size when you only map size, but it will give both to this variable.
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = cty, size = cty))
```

5. The stroke aesthetic changes the width of the border of each point. It works for every shape in the diagram in the R for Data Science reading. Some shapes do look better when increasing the stroke, while some become more of a blob quicker.
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy,  stroke = 10), shape = 12)
```

6. If you just assign an aesthetic without assigning an x and y, it will give you an error. If you do assign an x and y, then it will assign the aesthetic according to the requirements you state. For example, the question asks us to test color = displ < 5. As can be seen in the graph below, it assigns all points that have a displ less than 5 to one color and everything else another color. The same works for shape and size, but it will give you a warning that size is not recommended.
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = displ < 5))
```

3.5.1

4. The immediate advantage I can see by using facets instead of colors is that you can easily separate out each type. In this case, we can clearly see where the points are for each class of car. Another one, is that each subplot is less cluttered. The disadvantage I can see is that it may be a bit more difficult to compare types as you'll need to take a look at two subplots as opposed to one.  

In regards to a larger dataset, it depends on what that entails. If this means that there are more classes of cars, then I think I'd prefer to use color as having too many facets can be hard to read. If it means that there are simply more entries, but no increase in classes, I believe facet will be easier to read as each subplot will be less cluttered.
```{r}
ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```

5. nrow assigns the number of rows you want (so in the previous question, nrow = 2 gives us two rows). ncol assigns the number of columns of subplots there are (previous question had 4 columns, but we didn't need put it in).   

Other options that affect the layout are if we add another variable to the facet (I understand that we can also use facet_grid instead). You can also use dir to change the direction. A facet_grid does not accept nrows or ncols as arguments because the number of rows and columns is already determined by the number of unique types in each class. In the second facet below, you can see since drv has 3 types, it determines that there are 3 rows. There are 7 types of classes, so that determines the columns.
```{r}
ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, dir = "v")
```

```{r}
ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv ~ class)
```