---
title: "COMPSCIX 415.2 Homework 5/Midterm"
author: "Jonathan Lee"
date: "3/5/2018"
output:
  html_document:
    toc: TRUE
    self_contained: TRUE
---
[GitHub Link](https://github.com/JonathanLee90/compscix-415-2-assignments)
```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
```

###The tidyverse packages

1. Plotting - **ggplot2**  
Data munging/wrangling - **dplyr**  
Reshaping - **tidyr**  
Importing/exporting data - **readr**  

2. Plotting - **ggplot2** - ```geom_point()```, ```geom_smooth()```  
Data munging/wrangling - **dplyr** - ```glimpse()```, ```summarise()```  
Reshaping - **tidyr** - ```gather()```, ```spread()```  
Importing/exporting data - **readr** - ```read_csv()```, ```read_delim()``` 

###R Basics

1. This is fixed by taking out the ```!```.
```{r}
My_data.name___is.too00ooLong <- c( 1 , 2   , 3 )
```

2. This is fixed by changing the ```C``` to a lower case ```c``` and by adding a single quotation mark after ```'it``` to make it ```'it'```.
```{r}
my_string <- c('has', 'an', 'error', 'in', 'it')
```

3. Due to the ```3``` and ```4``` being in single quotes, it turns all the values in the vector to characters.
```{r}
my_vector <- c(1, 2, '3', '4', 5)
my_vector
glimpse(my_vector)
```

###Data import/export

1.
```{r}
rail_trail <- read_delim("E:/Chrome Downloads/rail_trail.txt", "|")
glimpse(rail_trail)
```

2. 
```{r}
saveRDS(rail_trail, file = "E:/Chrome Downloads/rail_trail.rds")
rail_trail_RDS <- read_rds("E:/Chrome Downloads/rail_trail.rds")
glimpse(rail_trail_RDS)
```

###Visualization

1. 
   * The circles don't provide a good representation of amount. Bars would be a better way.
   * The color scheme doesn't provide anything either. I'd perhaps have more differing colors between men and women.
   * Although the top does state that the numbers are percents, due to the numbers not adding up to 100%, people may think these numbers represent the amount of voters not the percentage.

2. 
```{r}
  ggplot(data = diamonds) +
    geom_boxplot(mapping = aes(x = cut, y = carat, fill = color), position = "identity") +
    xlab("CUT OF DIAMOND") + 
    ylab("CARAT OF DIAMOND") +
    coord_flip()
```

3. To me, when the colors are all in the same area, it doesn't provide much information. I have taken out the position argument and this way we can see how each color compares.
```{r}
  ggplot(data = diamonds) +
    geom_boxplot(mapping = aes(x = cut, y = carat, fill = color)) +
    xlab("CUT OF DIAMOND") + 
    ylab("CARAT OF DIAMOND") +
    coord_flip()
```

###Data munging and wrangling

1. I would say this data is not tidy. We need to spread out the type column.

```{r}
table2 %>%
  spread(key = type, value = count)
```

2. 

```
diamonds %>%
  mutate(price_per_carat = price / carat)
```

3. The n column is the amount of diamonds in each cut category, and proportion is the proportion when compared to all the cuts together.
```{r}
diamonds %>%
  filter(price > 10000 & carat < 1.5) %>%
  count(cut) %>%
  mutate(proportion = n / sum(n))
```

* These results make sense to me because as we are filtering only diamonds that cost over $10,000 while having a carat under 1.5, this means that the cut must be a higher caliber to justify the price.
* I would say perhaps we should be wary of the Fair numbers as there are not too many of them. 

###EDA

1. It appears that the time period is from 1/1/2000 - 7/31/2015.
```{r}
txhousing %>%
  group_by(year, month) %>%
  summarise()
```

2. There are 46 cities represented.
```{r}
length(unique(txhousing$city))
```

3. Houston in July 2015 had the most sales at 8945 sales.
```{r}
txhousing %>%
  arrange(desc(sales))
```

4. I think there is a positive correlation between sales and listings. I think the more listings there are, the more sales there will be. As you can see in the plot below, there is a positive correlation.

```{r warning=FALSE, message=FALSE}
ggplot(data = txhousing) +
  geom_point(mapping = aes(x = listings, y = sales)) +
  geom_smooth(mapping = aes(x = listings, y = sales)) 
```

5. Please refer to the table below, in the Proportion column.
```{r}
txhousing %>%
  group_by(city) %>%
  count(NA_Count = sum(is.na(sales))) %>%
  mutate(Proportion = NA_Count / n)
```

6. 

* I didn't really understand this question, but it doesn't appear the distribution is any different if you ```group_by``` city or not.
```{r}
txhousing %>%
  filter(sales > 500) %>%
  group_by(city) %>%
  ggplot() +
  geom_bar(mapping = aes(median)) +
  facet_wrap(~city)

txhousing %>%
  filter(sales > 500) %>%
  ggplot() +
  geom_bar(mapping = aes(median)) +
  facet_wrap(~city)
```

* Looking at the distributions, I would probably take a look at Arlington and Montgomery County since they both have a median price much higher than the rest of the distribution.

* With less than 500 sales, we would have a smaller sample size, which could result in some outliers.